An Empirical Analysis of the Role of Energy in Economic Growth

### 2015-01-15 Articles/Article_EnerEcon_2014/EconGrowth4.Rnw
Adding boundary models to paper.
Working on CES boundary models.

The fit with lowest $sse$ of all above trials 
is deemed the winning model to be presented in graphs.

>>>>

****

In addition to the above trials, we fit along all boundaries.
Table~\ref{tab:CES_boundary_models} shows the degenerate forms of CES on each boundary.
Equation~\ref{eq:ces_generic} accompanies Table~\ref{tab:CES_boundary_models}
and provides the generic CES equation
in which factors of production ($x_1$, $x_2$, $x_3$) 
are permutations of ($k$, $l$, $e$).
%
\begin{equation} \label{eq:ces_generic}
  y = \gamma A \left\{ \delta \left[ \delta_1 x_1^{-\rho_1} 
      + \left( 1 - \delta_1 \right) x_2^{-\rho_1} \right]^{\rho/\rho_1}  
          + \left( 1 - \delta \right) x_3^{-\rho}  \right\} ^ {-1/\rho} \; ,
\end{equation}
%
In the parameter columns of Table~\ref{tab:CES_boundary_models}, 
``---'' indicates that a parameter is unknowable on that boundary
(because it has been eliminated from the model), and
an empty space indicates that the parameter is to be estimated on that boundary.

\begin{table} \caption{Boundary models for the CES equation.} 
\label{tab:CES_boundary_models} 
  \begin{center}
    \begin{tabular}{c c c c l} 
      \toprule
      $\delta_1$  & $\delta$   & $\sigma_1$ & $\sigma$ & Boundary model \\
      \midrule
      1           & 1          & ---        & ---      & $y = \gamma A x_1$ \\
      0           & 1          & ---        & ---      & $y = \gamma A x_2$ \\
      ---         & 0          & ---        & ---      & $y = \gamma A x_3$ \\
      ---         & 1          & 0          & ---      & $y = \gamma A \min (x_1, \, x_2)$ \\
      0           & ---        & ---        & 0        & $y = \gamma A \min (x_2, \, x_3)$ \\
      1           & ---        & ---        & 0        & $y = \gamma A \min (x_1, \, x_3)$ \\
      ---         & ---        & 0          & 0        & $y = \gamma A \min (x_1, \, x_2, \, x_3)$ \\
%
                  & 1          & $\infty$   & ---        
            & $y = \gamma A \left[ \delta_1 x_1 + (1 - \delta_1) x_2 \right]$ \\
%
      0           &            & ---        & $\infty$        
            & $y = \gamma A \left[ \delta x_2 + (1 - \delta) x_3 \right]$ \\
%
      1           &            & ---        & $\infty$        
            & $y = \gamma A \left[ \delta x_1 + (1 - \delta) x_3 \right]$ \\
%
                  &            & $\infty$   & $\infty$        
            & $y = \gamma A \left\{ \delta \left[ \delta_1 x_1 + \left( 1 - \delta_1 \right) x_2 \right] 
                    + \left( 1 - \delta \right) x_3  \right\}$ \\
%
      ---         &            & 0          & $\infty$        
            & $y = \gamma A \left[ \delta \min (x_1, \, x_2) + \left( 1 - \delta \right) x_3  \right]$ \\
%
                  & ---        & $\infty$   & 0
            & $y = \gamma A \min \left[ \delta_1 x_1 + \left(1 - \delta_1 \right) x_2, \, x_3  \right]$ \\
%
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

****

The fit with lowest $sse$ of all above trials 
is deemed the winning model and presented in graphs.
